Quantifying unmet ICU beds in tertiary hospitals in urban India using Prospective Score Matching 

### 2022-09-19 manuscript.Rmd
tabellerna med nu.
det gör lite ont i ögonen att titta på dem just nu tyvärr, formatering har varit prio 2 jag ville bara presentera datan från förra veckan för diskussionen idag 19/9

tab.1_cap <- table_nums(name = "tab_1", 
                        caption = "Data types collected in the TITCO1 dataset")

                     knitr::kable(table1_1, "simple")

@@

tab.2_cap <- table_nums(name = "tab_2", 
                        caption = "Means and standard devations of quantitative variables of ICU and non-ICU admitted patients, respectively")

                     knitr::kable(table3, "simple"),

@@

tab.3_cap <- table_nums(name = "tab_3", 
                        caption = "P- and t-values of the quantitative values in comparison of non-ICU and ICU patients")

                     knitr::kable(statresult, "simple"),

@@

For the qualitative data, the propensity of each parameter to get a patient admitted to the ICU is in relation to the proportion of patients that were admitted to the ICU from the whole TITCO1 data set, about a third. If considerably more than a third of each qualitative parameter are admitted to the ICU, then that parameter is of interest. The proportions are presented in tab.4_cap <- table_nums(name = "tab_4", 
                        caption = "Proportion of patients admitted to the ICU for all variants of all quuantitative variables")

                     knitr::kable(qualitativetable, "simple"),

>>>>

```{r}
setwd("C:/Users/maria/Downloads/Packt Learning RStudio for R Statistical Computing 2012 RETAIL eBook-repackb00k/unmet-ICU-beds")
load("table1_1.rdata")

knitr::kable(table1_1, caption = "Data types collected in the TITCO1 dataset")
```

@@

```{r}
setwd("C:/Users/maria/Downloads/Packt Learning RStudio for R Statistical Computing 2012 RETAIL eBook-repackb00k/unmet-ICU-beds")
load("table3.rdata")

knitr::kable(table3, caption = "Means and standard devations of quantitative variables of ICU and non-ICU admitted patients, respectively")
```

@@

```{r}
setwd("C:/Users/maria/Downloads/Packt Learning RStudio for R Statistical Computing 2012 RETAIL eBook-repackb00k/unmet-ICU-beds")
load("statresult.rdata")

knitr::kable(table3, caption = "P- and t-values of the quantitative values in comparison of non-ICU and ICU patients")
```

@@

For the qualitative data, the propensity of each parameter to get a patient admitted to the ICU is in relation to the proportion of patients that were admitted to the ICU from the whole TITCO1 data set, about a third. If considerably more than a third of each qualitative parameter are admitted to the ICU, then that parameter is of interest. The proportions are presented in

```{r}
setwd("C:/Users/maria/Downloads/Packt Learning RStudio for R Statistical Computing 2012 RETAIL eBook-repackb00k/unmet-ICU-beds")
load("qualitativetable.rdata")

knitr::kable(qualitativetable, caption = "Proportion of patients admitted to the ICU for all variants of all quuantitative variables")
```
